Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations

### 2025-10-16 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, a lot of changes

        \begin{theorem}[inexact Moreau decomposition]

@@

        \begin{align}

@@

@@

\section{Linear convergence for the proximal problem}

@@

    The inner loop of the algorithm evaluates $x_k \approx_\epsilon T_{(B + \rho)}(y_k)$ for a given value of $\epsilon, B + \rho$ and $y_k$. 
    In this section, we will derive the sufficient conditions for linear convergence rate of the proximal gradient method can attain linear convergence rate for optimizing the dual formulation $\Psi_\lambda$ \eqref{eqn:dual-pp} of the proximal point problem. 
    To attain $x_k$, one approach is to utilize Theorem \ref{thm:dlty-gap-inxt-pp} numerically, usually using iterative algorithms. 
    The following assumption places additional assumption to the proximal problem for the inner loop. 

@@

            The $g^\star$ is an indicator function which represents a box constraint. 

@@

            The error bound constant $\gamma$ is very difficult to obtain an lower estimate in practice. 

@@

        \begin{proposition}[scenario I, 1-norm penalization]\label{prop:inn-loop-lin-cnvg}

        \end{proposition}
        \begin{definition}[piecewise linear-quadratic function {\cite[Definition 10.20]{rockafellar_variational_1998}}]
            A function $f: \RR^n \rightarrow \overline \RR$ is piecewise linear-quadratic when $\dom f$ is the union of finitely many piecewise polyhedral set, such that on each polyhedral partition of $f$ there exists $\alpha \in \RR, a \in \RR^n$, $C\in \RR^{n \times n}$ as a symmetric matrix is where $f$ has the representation $x \rightarrow \langle x, Cx\rangle + \langle a, x\rangle + c$. 
        \end{definition}
        The following proposition characterizes another case where error bound conditions of problem problem holds. 
        \begin{proposition}[convex PLQ proximal problem]\label{prop:plq-pp}

@@

        \end{example}
    \subsection{Inner loop complexity}
        In this section, we will estimate the total number of iterations in the inner loop to achieve a certain accuracies $\epsilon$ on primal objective $\Phi_\lambda$ of the proximal problem for some given $\lambda > 0$. 
        We will specify the context for parameters $\epsilon, \lambda$ in relation to the outer problem of obtaining $x_k \approx_{\epsilon_k} T_{B_k + \rho_k}(y_k)$.

>>>>

        \begin{theorem}[inexact Moreau decomposition]\label{thm:inxt-moreau-decomp}

@@

        \begin{align}\label{eqn:duality-gap-pp}

@@

            The proof of $(a) \implies (b)$, and the case when $(a)\iff (b)$, we refer readers to Villa et al. \cite[ Proposition 2.3]{villa_accelerated_2013}, and to show $(b) \iff (c)$ use Theorem \ref{thm:inxt-moreau-decomp}. 

@@

\section{Linear convergence for the proximal problem in the inner loop}

@@

    As an important reminder, we will fix the vector $y \in \RR^n$, which is in the inexact proximal problem as a constant in this entire section. 
    The inner loop of the algorithm is another algorithm that evaluates $x_k \approx_\epsilon T_{(B_k + \rho_k)}(y_k)$ for a given value of $\epsilon, B + \rho$ and at the point $y_k$. 
    To accomplish, let $\lambda = (B_k + \rho_k)^{-1}$, the algorithm needs to resolve the following equivalent inexact proximal point problem: 
        x_k \approx_\epsilon \hprox_{\lambda g}(y_k - \lambda \nabla f(y_k)). 
    Unfortunately recall that $g = \omega \circ A$ in the context of the outer loop hence it's impossible to directly evaluate the proximal operator of $g$ and hence we optimize the function $\Phi_\lambda$ as given by \eqref{eqn:primal-pp}. 
    In this section, we will show that there exists an algorithm generating the sequences $z_n, v_n$ such that $\mathbf G_\lambda (z_n, v_n)$ converges linearly if $\Psi_\lambda$ satisfies the error bound conditions. 
    Using results available in the literature, we will characterize the exact scenarios of $\omega \circ A$ when this is possible to achieve. 
    To start, the following assumption is the general error bound condition of a convex with additive composite structure. 

@@

            The $g^\star$ is an indicator of a polytope constraint. 

@@

            It is very difficult to obtain a lower estimate for $\gamma$ in practice. 

@@

        \begin{proposition}[sufficient conditions of linear convergence of the inner loop]\;\label{prop:inn-loop-lin-cnvg}\\
            Consider the following proximal problem: 
                \item The primal proximal problem $\Phi_\lambda(u) = \frac{1}{2\lambda}\Vert u - y\Vert^2 + \omega(Au)$.
                \item The dual proximal problem $\Psi_\lambda(v) = f(v) + g(v)$ where \\ $f(v) := \frac{1}{2\lambda}\left\Vert \lambda A^\top v - y\right\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2, g(v) := \omega^\star(v)$. 
            If, $\Psi_\lambda$ satisfies Assumption \ref{ass:eb-for-pp}. 
            Let $L_1$ be the global Lipschitz continuity constant of $\Phi_\lambda$ which it has in this case. 
            Let $\tau \ge L, \epsilon \ge 0$, $v_0 \in \dom \Psi_\lambda$ be an initial condition for an algorithm that satisfies Definition \ref{def:ista} with $F(v) = f(v) + g(v)$ and let the iterates $(v_n)_{n \ge 0}$ be generated by it. 
            Then, there exists a minimizer $\bar v$ for $\Psi_\lambda$, and the followings are true: 
                \item The sequence $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$ converges linearly to zero. \label{prop:inn-looplin-cnvg-item1}
                \item If we choose $z_n := y - \lambda A^\top v_n$, and $\bar z := y - \lambda A^\top \bar v$, then $\Phi_\lambda(z_n) - \Phi_\lambda(\bar z)$ converges linearly. \label{prop:inn-looplin-cnvg-item2}
                \item The duality gap satisfies for all $n \ge 0$ the inequality 
                $$\mathbf G_\lambda(z_n, v_n) \le \left(1 - \frac{\gamma_\lambda}{2\tau}\right)^{n/2}\left(1 + L_1\sqrt{2 \lambda}\right)(\Psi_\lambda(v_0) - \Psi_\lambda(\bar v)).$$
                \label{prop:inn-looplin-cnvg-item3}
                \item If $\mathbf G_\lambda(z_n, v_n) \le \epsilon$, then $z_n \approx_\epsilon \hprox_{\lambda g}(y)$. 
                \label{prop:inn-looplin-cnvg-item4}
            To see \ref{prop:inn-looplin-cnvg-item1}, the sequence $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$ has linear convergence by Proposition \ref{prop:1nrm-prox-problem} because we assumed that $\Psi_\lambda$ satisfies Assumption \ref{ass:eb-for-pp}. 
            More precisely it has: 
            \begin{align}\label{ineq:inn-loop-lin-cnvg-pitem1}
                \Psi_\lambda(v_n) - \Psi_\lambda(\bar v) &\le 
                    1 - \frac{\gamma_\lambda}{2\tau}
                \right)^n
                    \Psi_\lambda(v_0) - \Psi_\lambda(\bar v)
            We will now proceed to proving \ref{prop:inn-looplin-cnvg-item2}. 
            Because the iterates are given by $z_n = y - \lambda A^\top v_n$, and $\bar z = y - \lambda A^\top \bar v$, it provides $\Phi_\lambda(z_n) - \Phi_\lambda(v_0)$, we can use Theorem \ref{fact:minimizing-dual-pp} which gives: 
                \Phi_\lambda(z_n) - \Phi_\lambda(\bar z) &\le L_1 \sqrt{2\lambda}\left(
                    \Psi_\lambda(v_n) - \Psi_\lambda (\bar v)
                L_1\sqrt{2\lambda} \left(
                    1 - \frac{\gamma_\lambda}{2\tau}
                \right)^{n/2}\left(
                    \Psi_\lambda(v_0) - \Psi_\lambda(\bar v)
                \right)^{1/2}. 
            At (1), we used convergence results from Theorem \ref{thm:lin-cnvg-ista-eb}. 
            To prove \ref{prop:inn-looplin-cnvg-item3}, by definition of duality gap in \eqref{eqn:duality-gap-pp} we have:
                \mathbf G_\lambda(z_n, v_n) 
                &\underset{(?)}{=} \Phi_\lambda(z_n) + \Psi_\lambda(v_n) + 0
                &= \Phi_\lambda(z_n) + \Psi_\lambda(v_n) - \Phi_\lambda(\bar z) - \Psi_\lambda(\bar v)
                &= \Phi_\lambda(z_n)- \Phi_\lambda(\bar z) + \Psi_\lambda(v_n) - \Psi_\lambda(\bar v)
                L_1 \sqrt{2\lambda}\left(
                    1 - \frac{\gamma_\lambda}{2\tau}
                \right)^{n/2}\left(
                    \Psi_\lambda(v_0) - \Psi_\lambda(\bar v)
                    1 - \frac{\gamma_\lambda}{2\tau}
                \right)^{n}\left(
                    \Psi_\lambda(v_0) - \Psi_\lambda(\bar v)
            To choose a feasible $v_0$, we can...
            \todoinline{
                REMEMBER TO FINISH IT. 
        \begin{definition}[piecewise linear-quadratic function {\cite[Definition 10.20]{rockafellar_variational_1998}}]
            A function $f: \RR^n \rightarrow \overline \RR$ is piecewise linear-quadratic when $\dom f$ is the union of finitely many piecewise polyhedral set, such that on each polyhedral partition of $f$ there exists $\alpha \in \RR, a \in \RR^n$, $C\in \RR^{n \times n}$ as a symmetric matrix is where $f$ has the representation $x \rightarrow \langle x, Cx\rangle + \langle a, x\rangle + c$. 
        The following proposition characterizes another case where error bound conditions of problem holds. 
        \begin{proposition}[convex PLQ proximal problem]\label{prop:plq-pp}

@@

        \end{example}
    \subsection{Inner loop complexity}
        In this section, we will estimate the total number of iterations in the inner loop to achieve a given accuracy $\epsilon$ on primal objective $\Phi_\lambda$ of the proximal problem for some given $\lambda > 0$. 
        We will specify the context for parameters $\epsilon, \lambda$ in relation to the outer problem of obtaining $x_k \approx_{\epsilon_k} T_{B_k + \rho_k}(y_k)$.

### 2025-10-16 Notebook LaTEX/R-WAPG/presentation-shorter.tex
>w<, a lot of changes

                        \item Retains convergence rate $\mathcal O(1/k^2)$ with $\theta_{k} = \frac{k - 2}{k + a - 1}$. 

@@

                    \item Has convergence rate $\mathcal O(1/k^{2b/3})$. 

@@

\section{References, acknowledgement and our draft on arxiv}
    \begin{frame}{Acknowledgements}
        \begin{tcolorbox}
            The research of HL and XW was partially supported by the NSERC Discovery Grant of Canada.
            \par
            We respectfully acknowledge that the UBC Okanagan academic campus is situated on the traditional, ancestral, unceded territory of the Syilx Okanagan Nation    
        \end{tcolorbox}
    \end{frame}
    \begin{frame}{Thanks for the participation. Merci pour les participations.}
        Our paper can be found on arxiv using the following QR code: 
        \begin{figure}
            \centering
            \includegraphics[width=15em]{assets/paper-qrcode.png}
        \end{figure}
        Questions?
    \end{frame}
    \begin{frame}{References}        
        \bibliography{references/R-WAPG.bib}
    \end{frame}

>>>>

                        \item It etains convergence rate $\mathcal O(1/k^2)$ with $\theta_{k} = \frac{k - 2}{k + a - 1}$. 

@@

                    \item It has convergence rate $\mathcal O(1/k^{2b/3})$. 

@@

\section{References, acknowledgement and our draft on arxiv}
    \begin{frame}{Acknowledgements}
        The research of HL and XW was partially supported by the NSERC Discovery Grant of Canada.
        \par
        We respectfully acknowledge that the UBC Okanagan academic campus is situated on the traditional, ancestral, unceded territory of the Syilx Okanagan Nation. 
    \end{frame}
    \begin{frame}{Thanks for the participation. Merci pour les participations.}
        Our paper can be found on arxiv using the following QR code: 
        \begin{figure}
            \centering
            \includegraphics[width=15em]{assets/paper-qrcode.png}
        \end{figure}
        Questions?
    \end{frame}
    \begin{frame}{References}        
        \bibliography{references/R-WAPG.bib}
    \end{frame}
